Introduction

### 2015-07-22 dissertation/papersincontext.tex
survey

>>>>

I committed to do the survey after Jürgen Umbrich challenged me to see
if the standards were actually followed. Rather than just survey the
usage for SPARQL Endpoints, I decided to do it for the breadth of the
Semantic Web. This resulted in a research track paper on the Extended
Semantic Web Conference 2015 entitled ``A Survey of HTTP Caching
Implementations on the Open Semantic Web'' with reference
\cite{kjernsmo_survey_2015} and a technical report
\cite{kjernsmo_add_survey_2015} that elaborates on data reduction
methods and statistical methods.

Although the support for caching headers are not yet widespread, it is
sufficient to perform experiments on real-world data.
